---
title: "beginning"
author: "Wells"
date: "2026-02-22"
output: html_document
---


###----------------------------------------------------###

# Starting Your Own Project: See beginning.rmd

###----------------------------------------------------###

If you are starting from scratch
Get your files into a folder, one article per file, and in raw .txt

```{r}
#text obtained with a web scraper
files <- list.files("./kamala_extracted_text", pattern="*.txt") |> 
  as.data.frame() |> 
  rename(filename = 1) |> 
  mutate(name = str_replace_all(filename, ".txt", "")) |> 
  mutate(name = str_replace_all(tolower(name), " ", "_")) |> 
  mutate(name = str_replace_all(name, "[[:punct:]]", "")) |> 
  arrange((name)) |> 
  mutate(index = row_number())
         
          
 #  #create an index with the file name
 # mutate(index = str_extract(filename, "\\d+")) |> 
 #  mutate(index = as.numeric(index))

kharris_index <- rio::import("./assets/DW_Kamala_Articles.xlsx") |> 
  mutate(name = str_replace_all(tolower(NAME), " ", "_")) |> 
  mutate(name = str_replace_all(name, "[[:punct:]]", "")) |> 
  arrange((name)) |> 
  mutate(index = row_number()) |> 
  distinct(name, .keep_all = TRUE) |> 
  mutate(DATE = case_when(
    str_detect(as.character(DATE), "2023-11-04") ~ as_datetime("2024-11-04"),
    TRUE ~ DATE
    ))
```

```{r}
final_index <- files |> 
  inner_join(kharris_index, by=c("name")) |> 
  mutate(filepath = paste0("./kamala_extracted_text/", filename)) |> 
  janitor::clean_names() |> 
  rename(index = index_x) |> 
  distinct(index, .keep_all = TRUE) |> 
  select(index, date,filename,url, filepath, filename)

#fact check
anti <- files |> 
  anti_join(kharris_index, by=c("name"))

```

#### Compile text into a single dataframe

```{r include=FALSE, echo=FALSE}
###
# Define function to loop through each text file 
###

create_article_text <- function(row_value) {
  
  #row_value is the single argument that is passed to the function
  # Take each row of the dataframe
  temp <- final_index |>
    slice(row_value)
  
  # Store the filename for  use in constructing articles dataframe
  temp_filename <- temp$filename
  
  # Create a dataframe by reading in lines of a given textfile
  # Add a filename column 
  articles_df_temp <- read_lines(temp$filepath) |>
    as_tibble() |>
    mutate(filename = temp_filename)
  
  # Bind results to master articles_df
  # <<- returns to global environment
  articles_df <<- articles_df |>
    bind_rows(articles_df_temp)
}

###
# Create elements needed to run function
###

# Create empty tibble to store results
articles_df <- tibble()
#running once to test
#create_article_text(2) 
# Create an array of numbers to loop through, from 1 to the number of rows in our index dataframe 
row_values <- 1:nrow(final_index)

###
# Execute function using lapply
# This loops through each row of the dataframe and append results to master file
###

lapply(row_values, create_article_text)
###
# Clean up articles_df and join to index dataframe
###

articles_df <- articles_df |>
  select(filename, sentence=value) |>
  inner_join(final_index)

```

#### Clean data

```{r}
phrases <- c("Date:" = "", 
            "Article Text:" = "",
            "Headline:" = "",
            "Already have an account?" = "", 
            "Your information could be the missing piece to an important story. Submit your tip today and make a difference." = "",
            "Stay up-to-date on the latestnews, podcasts, and more." = "",
  "https" = "")


harris_articles_df <- articles_df |> 
   mutate(sentence = str_replace_all(sentence, phrases))

#write.csv(harris_articles_df, "kharris_extracted_text_jan2025.csv")
```

<br> 

::: {style="text-align: center; color: #FF4500; font-weight: bold;"}
# Background Content
:::   





# cut

data cleaning that we wont discuss. keeping in case I need to redo 





#baltimore_collapsed <- baltimore |>
  # 1. Group by all metadata columns to preserve them
  group_by(
    filename, title, published_date, publication_location, 
    publication_4, length, section, 
    word_count, byline, headline, 
    index, filepath
  ) |> 
  
  # 2. Identify the boundaries of the actual article body
  # Start: row after "Body"
  # End: row before "Classification Language:"
  filter({
    body_start <- which(grepl("^Body", sentence, ignore.case = TRUE))
    class_end  <- which(grepl("^Language:", sentence, ignore.case = TRUE))
    
    # Logic: 
    # If "Body" exists, start after it; otherwise start at row 1.
    # If "Classification" exists, end before it; otherwise end at the last row.
    start_idx <- if(length(body_start) > 0) min(body_start) + 1 else 1
    end_idx   <- if(length(class_end) > 0) min(class_end) - 1 else n()
    
    row_number() >= start_idx & row_number() <= end_idx
  }) |>
  
  # 3. Collapse the remaining sentences into the 'text' column
  summarise(
    text = paste(sentence[!is.na(sentence)], collapse = " "), 
    .groups = "drop"
  )

# Preview result
head(baltimore_collapsed)

#write_csv(baltimore_collapsed, "assets/bmore_new.csv")



baltimore <- read_csv("assets/bmore.csv")
Fix dates

library(zoo)
baltimore <- baltimore |> 
  mutate(yearmo = as.yearmon(date))

baltimore <- baltimore |> 
  select(date, title, text, yearmo, everything())

baltimore <- baltimore |> 
  subset(select = -c(headline))

write_csv(baltimore, "assets/bmore.csv")

